%کلمات کلیدی انگلیسی
\latinkeywords{Reinforcement Learning, Deep Reinforcement Learning, 2D Soccer Simulation, Gym, One-On-One Soccer}
%چکیده انگلیسی

\en-abstract{
This page is accurate translation from Persian abstract into English.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract
This thesis explores deep reinforcement learning and its performance in scoring goals in one-on-one soccer situations. Initially, we examine the concepts of reinforcement learning and its fundamental principles to provide a comprehensive understanding of decision-making and machine learning in dynamic environments. Then, the 2D soccer simulation platform RoboCup, which we intend to use, is introduced. In this research, various reinforcement learning algorithms, including Deep Q-Networks, policy-based reinforcement learning, and other advanced approaches, have been reviewed to assess their impact on improving players' performance in scoring goals. A significant part of this research is devoted to establishing a standard method for conducting reinforcement learning in RoboCup soccer simulations using the Gym framework; this promises the integration and standardization of reinforcement learning methods in this field. Ultimately, we will see how the use of these algorithms can effectively help players make better decisions in one-on-one situations and score more goals. In addition, the thesis examines the impact of different algorithmic parameters and settings on the performance of reinforcement learning and offers solutions for performance improvement.
\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}